Instructions for TTO 2019 Proceedings

### 2021-06-30 article/test.tex
first iteration

\documentclass{article}
%\documentclass[a4paper,12pt,twoside]{book}
\usepackage{amsmath}
\usepackage{cite}
%\usepackage{tikz}
\usepackage{bm}
\usepackage{tikz,tkz-tab}
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{hyperref}
\usepackage{mathtools}
%\usepackage{subcaption}
\usepackage{color}
\usepackage{setspace}
\usepackage{empheq}
\usepackage{bbm, dsfont}
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{geometry}
\usepackage{enumitem} 
\usepackage[bottom]{footmisc}
\usetikzlibrary{arrows}
\usepackage{lscape}
\usepackage{tcolorbox}
\usepackage{caption}
%\usepackage{graphicx}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{cite}
\usetikzlibrary{shapes,snakes}
\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\diamond$}

\usepackage{titlesec}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\newtheorem{definition}{Definition}

\usetikzlibrary{positioning}
\tikzset{main node/.style={circle,draw,minimum size=0.5cm,inner sep=0pt},
            }

%-------------------------------------------
\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{assumption}{Assumption}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{observation}{Observation}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}
\title{Very Preliminary Draft}
\maketitle

%Using social media data to verify the platforms' regulation policies regarding misinformation"

@@

A number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.''  }

Section $230$ in the United States Communications Decency Act\footnote{Similar regulation exists in the European Union, see articles $12$ and $15$ of the E-commerce Directive (2000). } provides immunity for website platforms against the content created by users. Nevertheless, there is growing pressure for Mainstream Social Media Platforms (hereafter MSMP), such as Facebook, Twitter or Youtube, to moderate the available content. In particular, platforms seem to take explicit actions when content is in violation of local laws in different jurisdictions, e.g. laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws. Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}. We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}

@@

Furthermore, MSMP are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community standards of Facebook, see: \href{https://www.facebook.com/communitystandards/}{facebook.com/communitystandards/}. For the Twitter  Rules see: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}, and for Youtube community guidelines see: \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}.} While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries.

@@

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The rise of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. {\color{red} Fact-checkers + no laws or not so much.}

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. {\color{red} Say what they say they do + partnerships with fact-checkers + algorithms + community, Make point about ``recycling" existing policies (e.g. to tackle terrorism) and apply it to misinformation+ idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}

In the present article, we will explain how to verify with data mining MSMP's actions regarding content with low credibility or false information, through a series of examples for different actions and platforms. For the purpose of clarity, we only focus on three platforms: Facebook, Twitter and Youtube. Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited MSMP, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies. We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring. We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.  %the announced policy for a specific user was implemented or not.

%Second, we provide simple means to check how those policies are implemented in practice and discuss how to assess their impact, when possible.

%We do not aim for an exhaustive list of methods on how to investigate the platforms’ policies against misinformation, but rather to share the methods we currently know, and that we think can be useful to researchers or journalists interested in that question. We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.

\bigskip

@@

\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook. \\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content database  \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

 %We We are aware that other APIs or databases can be useful on that matter, but we will only mention here the ones about which we have some experience.

%CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages. BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.

%Section 230 in the US + EU 
%Pressure to moderate and mix-up of platforms with public square… 
%Rôle dans la production/médiation : P-M-R 
%Pourquoi faut-il vérifier leurs politiques ? D’une part parce que ce sont les plateformes elles-mêmes qui annoncent leurs effets. D’autre part beaucoup de choses indirectes. 
%
%Add disclaimer in a footnote early on in the document : document not meant to be an exhaustive overview of all the existing regulations and point to three or four main legal sources for exhaustive references.

%Such policies include the introduction of notices (Twitter, see link) or flags (Facebook, see…) to signal to users inaccurate or false content, the temporary or permanent suspension of accounts (Twitter) or pages (Facebook), reducing the visibility of posts or pages (Facebook), or blocking users from sharing specific URL links (see link). The objective of this article is twofold. First, we study the impact of a number of  implemented measures by mainstream platforms to tackle (mis)disinformation.

@@

@@

When an account is permanently suspended by Facebook, it disappears from the platform (so its data cannot be scrapped anymore), and its data also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.35]{./img/fb/fig1_fb.png}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

{\color{red} N.B. Manual decision, not the automatic strike system}
\begin{figure}
\centering
\includegraphics[scale=0.35]{./img/lifesite.jpg} 
\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

In this section, we discuss one case of temporary suspension on Twitter.\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account $@LifeSite$ via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

@@

In this section, we turn to the channel's temporary or permanent suspension policy of Youtube. Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed. For the second time the channel will start receiving strikes. A first strike results in limiting the access of the Youtube channel  for one week, like uploading videos, streaming and other activities. Then a second strike is similar but the suspension will be for two weeks. A third strike results in the termination of the channel. The strike count of a channel lasts 90 days.  In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.\footnote{See the ``Community Guidelines strike basics''. Youtube help, Google Developers,  \href{https://support.google.com/youtube/answer/2802032?hl=en. Accessed 21 6 2021}{https://support.google.com/youtube/answer/2802032?hl=en. Accessed 21 6 2021}.} To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two Youtube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{./img/oann/fig1_oann.png}
	\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.2]{./img/oann/fig3_oann.png}
	\includegraphics[scale=0.3]{./img/tony/fig3_tony.png}
	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), Twitter ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}. Panel (b): Tony Heller's tweet after getting suspended from Youtube, Twitter ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}.}
	\label{fig2_oann}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{./img/tony/fig1_tony.png}
	\includegraphics[scale=0.3]{./img/tony/fig2_tony.png}
	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Panel (b): accumulated view counts for videos uploaded by the same Youtube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}

@@

{\color{pink}The Beauty of life}

>>>>

%
% File tto2019.tex
%
%% Based on the style files for ACL 2019, ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{tto2019}
\usepackage{times}
\usepackage{latexsym}
\usepackage{multicol}
\usepackage{graphicx}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Instructions for TTO 2019 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

@@

A number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense.

Section $230$ in the United States Communications Decency Act\footnote{Similar regulation exists in the European Union, see articles $12$ and $15$ of the E-commerce Directive (2000). } provides immunity for website platforms against the content created by users. Nevertheless, there is growing pressure for Mainstream Social Media Platforms (hereafter MSMP), such as Facebook, Twitter or Youtube, to moderate the available content. In particular, platforms seem to take explicit actions when content is in violation of local laws in different jurisdictions, e.g. laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws. Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{https://transparency.fb.com/data/content\-restrictions}. We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{https://transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}

@@

Furthermore, MSMP are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community guidelines of Facebook, see: \href{https://www.facebook.com/communitystandards/}{https://www.facebook.com/communitystandards/}, for Twitter see: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}, and for Youtube see: \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}.} While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries. In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The rise of social networking platforms over the last decade in terms of number of users worldwide, has modified the information ecosystem in terms of production of information and its mediation. In particular, many users can now produce content which contains news related information without having to abide by strict editorial processes that ensure accuracy of information.

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general.

In this article, we will explain how to verify with data mining MSMP's actions regarding content with low credibility or false information, through a series of examples for different actions and platforms. For the purpose of clarity, we focus on three platforms: Facebook, Twitter and Youtube. Both Facebook and Youtube are in the top 3 most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}.

In this article, we survey a number of common policies used in order to tackle misinformation, across the three above cited MSMP, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. Second, we provide simple means to check how those policies are implemented in practice and discuss how to assess their impact, when possible. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.  %the announced policy for a specific user was implemented or not.  
\bigskip

@@

%\begin{table}[]
%\centering
%\begin{tabular}{|l|l|l|l}
%
%\hline
%&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
%Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook. \\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content database  \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
%\\ \hline
%Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
%Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
%\end{tabular}
%\caption{Data collection}
%\end{table}

@@

%\begin{figure}
%\centering
%\includegraphics[scale=0.35]{./img/lifesite.jpg} 
%\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
%\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
%\label{fig2}
%\end{figure}

\begin{figure}
\centering
\begin{multicols}{1}
    \includegraphics[scale=0.32]{./img/lifesite.jpg}\par 
    %\includegraphics[width=\linewidth]{./img/lifesite_rolling_7_lifesite.jpg}\par 
    \end{multicols}
\begin{multicols}{1}
   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
    \includegraphics[scale=0.32]{./img/lifesite_rolling_7_lifesite.jpg}\par
\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021.}
\label{fig2}
\end{figure}

In this section, we discuss one case of temporary suspension on Twitter.\footnote{See the official documentation on the Twitter's Help Center regarding account suspension: \href{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts}{https://help.twitter.com/en/managing-your-account/suspended-twitter-accounts }.} The Twitter account of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason of the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/}}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account $@LifeSite$ via the Twitter API, using the historical search endpoint.\footnote{See the documentation: \href{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}{https://developer.twitter.com/en/docs/twitter-api/tweets/search/api-reference/get-tweets-search-all}.} We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

@@

Unfortunately when an account is permanently suspended by Facebook, it disappears from the platform (so its data cannot be scrapped anymore), and its data also disappears from the CrowdTangle API.\footnote{CrowdTangle is a public insights tool owned and operated by Facebook, that exclusively tracks public content from Facebook public groups and pages.} For a previous research project\footnote{reference?}, we searched on CrowdTangle for public accounts sharing specific content associated with misinformation in November $2020$, and selected $94$ Facebook pages corresponding to our criteria. We then tried to collect these pages' posts in January $2021$, and discovered that $11$ pages could not be found anymore. This highlights an important issue when studying misinformation trends on Facebook: some data disappears from the CrowdTangle API as accounts are deleted or changed to {\it private}.

@@

%\begin{figure}
%	\centering
%	%\includegraphics[scale=0.35]{./img/fb/fig1_fb.png}
%	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
%	\label{fig1_fb}
%\end{figure}

\begin{figure}
\begin{multicols}{1}
    \includegraphics[scale=0.22]{./img/fb/fig1_fb.png}\par 
   % \includegraphics[width=\linewidth]{./img/lifesite_rolling_7_lifesite.jpg}\par 
    \end{multicols}
%\begin{multicols}{2}
   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
 %   \includegraphics[width=\linewidth]{./img/lifesite_rolling_7_lifesite.jpg}\par
%\end{multicols}
\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
\label{fig1_fb}
\end{figure}

In this section, we turn to the channel temporary or permanent suspension policy of Youtube. Whenever a channel publishes a video that violates the community guidelines for the first time they will  usually receive a warning and the content will be removed. For the second time the channel will start receiving strikes. A first strike results in limiting the access of the Youtube channel  for one week, like uploading videos, streaming and other activities. Then a second strike is similar but the suspension will be for two weeks. A third strike results in the termination of the channel. The strike count of a channel lasts 90 days.  In the special case, where a video is in extreme violation of the guidelines, the publishing channel may get terminated without a warning.\footnote{See the ``Community Guidelines strike basics''. Youtube help, Google Developers,  \href{https://support.google.com/youtube/answer/2802032?hl=en. Accessed 21 6 2021}{https://support.google.com/youtube/answer/2802032?hl=en. Accessed 21 6 2021}.} To illustrate the implementation of this policy we provide two examples for the temporary suspension of the following two Youtube channels: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.

@@

%\begin{figure}
%	\centering
%	%\includegraphics[scale=0.25]{./img/oann/fig1_oann.png}
%	%\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
%	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
%	\label{fig1_oann}
%\end{figure}

\begin{figure}
\centering
\begin{multicols}{1}
    \includegraphics[scale=0.3]{./img/oann/fig1_oann.png}\par 
    %\includegraphics[width=\linewidth]{./img/lifesite_rolling_7_lifesite.jpg}\par 
    \end{multicols}
\begin{multicols}{1}
   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
    \includegraphics[scale=0.3]{./img/oann/fig2_oann.png}\par
\end{multicols}
\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
\label{fig1_oann}
\end{figure}

@@

%\begin{figure}
%	\centering
%	%\includegraphics[scale=0.2]{./img/oann/fig3_oann.png}
%	%\includegraphics[scale=0.3]{./img/tony/fig3_tony.png}
%	\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), see: \href{https://twitter.com/OANN/status/1372238828425998336}{https://twitter.com/OANN/status/1372238828425998336}. Panel (b): Tony Heller's tweet after getting suspended from Youtube, see \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{https://twitter.com/Tony\_Heller/status/1310703852769796097}.}
%	\label{fig2_oann}
%\end{figure}

\begin{figure}
\centering
\begin{multicols}{1}

    \includegraphics[scale=0.25]{./img/oann/fig3_oann.png}\par 
    %\includegraphics[scale=0.2]{./img/tony/fig3_tony.png}\par 
    \end{multicols}
\begin{multicols}{1}

   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
    \includegraphics[scale=0.25]{./img/tony/fig3_tony.png}\par
\end{multicols}
\caption{Panel (a): Tweet announcing moving to rumble by OANN (Twitter), tweet ID \href{https://twitter.com/OANN/status/1372238828425998336}{1372238828425998336}. Panel (b): Tony Heller's tweet after getting suspended from Youtube, tweet ID \href{https://twitter.com/Tony\_Heller/status/1310703852769796097}{1310703852769796097}. }
\label{fig2_oann}
\end{figure}

@@

%\begin{figure}
%	\centering
%	%\includegraphics[scale=0.3]{./img/tony/fig1_tony.png}
%	%\includegraphics[scale=0.3]{./img/tony/fig2_tony.png}
%	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Panel (b): accumulated view counts for videos uploaded by the same Youtube channel. The date corresponds to the videos’  publishing date. 
%}
%	\label{fig1_tony}
%\end{figure}

\begin{figure}
\centering
\begin{multicols}{1}

    \includegraphics[scale=0.33]{./img/tony/fig1_tony.png}\par 
    %\includegraphics[scale=0.2]{./img/tony/fig3_tony.png}\par 
    \end{multicols}
\begin{multicols}{1}

   % \includegraphics[width=\linewidth]{./img/lifesite.jpg}\par
    \includegraphics[scale=0.33]{./img/tony/fig2_tony.png}\par
\end{multicols}
\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Panel (b): accumulated view counts for videos uploaded by the same Youtube channel. The date corresponds to the videos’  publishing date. 
 }
\label{fig2_oann}
\end{figure}

@@

The Beauty of life
